Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-20 ICML-submission/related-work.tex
Update related-work.tex
Slightly edited the last two paragraphs to make them shorter

There is a large body of literature on the contextual bandits
problem~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
given a policy class $\Pi$, and at each timestep $t$, an example $x_t$ is shown,
with an associated cost vector $c_t$ hidden. The learner then takes an action
$\widehat{y}_t$, and observes the incurred cost $c_t(\widehat{y}_t)$. The goal
of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) -
\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$. The online bandit multiclass
learning problem can be seen a special case of the contextual bandits problem, where the
cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$, and the
policy class $\Pi$ is the set of linear classifiers $\cbr{x \mapsto \argmax_y
(Wx)_y: W \in \R^{k \times d}}$. A series of works in the contextual bandits
learning literature focus on
oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they assume access to
a policy optimization oracle that can return the policy in $\Pi$ that minimizes
its empirical cost on any set of cost-sensitive examples, and the algorithm only
calls the oracle a polynomial number of times. However, these algorithms are not
truly computationally efficient in our setting, as it is NP-hard in general to
find a linear classifier that minimizes the empirical cost over a set of
examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.

@@

Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
contextual bandits with surrogate losses, focusing on regrets of the form
$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K}
\sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$, where $\calF$ contains score functions
$f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac
s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
information-theoretic regret upper bounds under various settings of $\calF$.
On the other hand, it gives an
efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$. A direct
application of this result to \textsc{Online Bandit Multiclass Linear
Classification} yields an algorithm with a $O(\sqrt{T})$ mistake bound in the
strongly linearly separable setting.

>>>>

There is a large body of literature on the contextual bandits
problem~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
given a policy class $\Pi$, and at each timestep $t$, an example $x_t$ is shown,
with an associated cost vector $c_t$ hidden. The learner then takes an action
$\widehat{y}_t$, and observes the incurred cost $c_t(\widehat{y}_t)$. The goal
of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) -
\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
%%%%%
The bandit multiclass
learning problem can be seen as a special case,
% of the contextual bandits problem, 
where the
cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$, and the
policy class $\Pi$ is the set of linear classifiers $\cbr{x \mapsto \argmax_y
(Wx)_y: W \in \R^{k \times d}}$. A series of works in the contextual bandits
learning literature 
%focus on oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
%Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
%Syrgkanis-Krishnamurthy-Schapire-2016,
%Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they 
assume access to
a policy optimization oracle that returns a policy in $\Pi$ that minimizes
its empirical cost on any set of cost-sensitive examples, and 
%the
construct algorithms that call 
%algorithm only calls 
the oracle a polynomial number of times%
~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
%%%%%
However, these algorithms are not
truly computationally efficient in our setting, as it is NP-hard in general to
find a linear classifier that minimizes the empirical cost over a set of
examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.

@@

Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
contextual bandits with surrogate losses, focusing on regrets of the form
$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K}
\sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$, where $\calF$ contains score functions
$f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac
s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
information-theoretic regret upper bounds
%%%%%
%under
 for
%%%%%
various settings of $\calF$. On the other hand, it gives an efficient algorithm 
%%%%%
with an 
%%%%%
$O(\sqrt{T})$ regret against the benchmark of
$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$. A direct
application of this result to \textsc{Online Bandit Multiclass Linear
Classification} 
%%%%%
%yields 
gives
%%%%%
an algorithm with $O(\sqrt{T})$ mistake bound in the
strongly linearly separable %%%%%
case.
%%%%%
